---
title: "Cd dynamics"
author: "Donghao Xu"
date: "2025-12-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction
This R markdown file contains the scripts for the data analysis done for the study `Large-scale impacts of nutrient management strategies on acidification-induced risks for crop yields and food quality by cadmium` written by Xu et al. (2025).
Source data used in this code can be found in Zenodo (DOI: 10.5281/zenodo.18078637)

#1. Cadmium dynamic simulations

## 1.1 Build Cd regression model
```{r}
# load packages
library(data.table)

# load database
pri_df <- fread("model_data/Cd_regression_data.csv", header=TRUE, sep=",", skip = 2, fill=TRUE) 

# add log transformations
pri_df[,logclay := log10(Clay)]
pri_df[,logSOC := log10(OC/10)]
pri_df[,logsolutionCd := log10(SoilCdavi*10)]
pri_df[,logsoilCd := log10(SoilCdtot)]

#**Derive soil-solution regression model**

# Select relevant columns and remove missing values
soil_solution <- pri_df[, .(logsolutionCd, logsoilCd, logSOC, logclay, pH, source, land_use, code)]
soil_solution <- na.omit(soil_solution)

#**Multiple linear regression for raw crop data**
ML_solution <- lm(logsolutionCd ~ logsoilCd + logSOC + logclay + pH + land_use - 1, data = soil_solution)
summary(ML_solution)

#**Clean solution data based on Cook distance**

# Calculate Cook's Distance
cook_dist <- cooks.distance(ML_solution)

# Identify high Cook's Distance points
high_cook <- which(cook_dist > 4 / length(cook_dist))

# Plot Cook's Distance
plot(cook_dist, type = "h", main = "Cook's Distance", ylab = "Cook's Distance")
abline(h = 4 / length(cook_dist), col = "red", lty = 2)  # Threshold line

# Remove high Cook's Distance points
clean_solu_data <- soil_solution[-high_cook]

#**Multiple regression model for cleaned data**
ML_solution_clean <- lm(logsolutionCd ~ logsoilCd + logSOC + logclay + pH + land_use - 1, data = clean_solu_data)
summary(ML_solution_clean)

# Add predictions
clean_solu_data[, pred := predict(ML_solution_clean)]

# Mark outliers
soil_solution[, outlier := "prediction"]
soil_solution[high_cook, outlier := "outlier"]

#**Calculate Normalized Mean Absolute Error (NMAE), Normalized Root Mean Square Error (NRMSE), and the R-squared **
solu_nmae <- mean(abs(clean_solu_data$pred - clean_solu_data$logsolutionCd)) / mean(abs(clean_solu_data$logsolutionCd))  # NMAE in percentage
solu_nrmse <- sqrt(mean((clean_solu_data$pred - clean_solu_data$logsolutionCd)^2)) / mean(abs(clean_solu_data$logsolutionCd))  # NRMSE in percentage

# Extract coefficients for the regression equation
solu_coeffs <- round(coef(ML_solution_clean), 2)

# Get regression equations and build the regression equation as a string
solu_regression_eq <- paste0("logsolutionCd = ",
                              solu_coeffs["logsoilCd"], "*logsoilCd",
                              solu_coeffs["logSOC"], "*logSOC",  solu_coeffs["logclay"], "*logclay", "\n",
                              "                       ", solu_coeffs["pH"], "*pH+", 
                              ifelse("land_usePaddy" %in% names(solu_coeffs), solu_coeffs["land_usePaddy"], 0), "*paddy+",
                              ifelse("land_useUpland" %in% names(solu_coeffs), solu_coeffs["land_useUpland"], 0), "*upland"
                            )

# Derive predictions based on the multiple linear regression
soil_solution[land_use == "Upland", pred := solu_coeffs["logsoilCd"]*logsoilCd + solu_coeffs["logSOC"]*logSOC + solu_coeffs["logclay"]*logclay +
                                            solu_coeffs["pH"]*pH + solu_coeffs["land_useUpland"]]
soil_solution[!land_use == "Upland", pred:= solu_coeffs["logsoilCd"]*logsoilCd + solu_coeffs["logSOC"]*logSOC + solu_coeffs["logclay"]*logclay + 
                                            solu_coeffs["pH"]*pH + solu_coeffs["land_usePaddy"]]


#** Derive soil-crop regression model**
rice_data <- pri_df[
  complete.cases(RiceCd, SoilCdtot, logSOC, source, logclay, pH, code), 
  .(logcropCd = log10(RiceCd), crop = "grain",
    logsoilCd, logSOC, source, logclay, pH, code)]

# Process straw_data
straw_data <- pri_df[
  complete.cases(StrawCd, SoilCdtot, logSOC, source, logclay, pH, code), 
  .(logcropCd = log10(StrawCd), crop = "straw",
    logsoilCd, logSOC, source, logclay, pH, code)]

crop_data <- rbind(na.omit(rice_data), na.omit(straw_data))

#**Multiple linear regression for raw crop data**
ML_crop = lm(logcropCd ~ logsoilCd + logSOC+logclay+pH+crop-1, data = crop_data)
summary(ML_crop)

#**Clean crop data based on Cook distance**
# Get Cook's Distance
cook_dist <- cooks.distance(ML_crop)

# Identify points with high Cook's Distance (e.g., greater than 4/n)
high_cook <- which(cook_dist > 4/length(cook_dist))

# Plot Cook's Distance
plot(cook_dist, type = "h", main = "Cook's Distance", ylab = "Cook's Distance")
abline(h = 4/length(cook_dist), col = "red", lty = 2)  # Threshold line

crop_data$outlier <- "prediction"
crop_data[high_cook, ]$outlier <- "outlier"

# Remove rows corresponding to identified outliers (example: based on Cook's Distance)
clean_crop_data <- crop_data[-high_cook, ]

#**Multiple relationship for cleaned data**
ML_crop_clean = lm(logcropCd ~ logsoilCd + logSOC+logclay+pH+crop-1, 
                   data = clean_crop_data)
summary(ML_crop_clean)

# Add predictions
clean_crop_data[, pred := predict(ML_crop_clean)]

#**Calculate Normalized Mean Absolute Error (NMAE), Normalized Root Mean Square Error (NRMSE), and the R-squared **
crop_nmae <- mean(abs(clean_crop_data$pred - clean_crop_data$logcropCd)) / mean(abs(clean_crop_data$logcropCd))  # NMAE in percentage
crop_nrmse <- sqrt(mean((clean_crop_data$pred - clean_crop_data$logcropCd)^2)) / mean(abs(clean_crop_data$logcropCd))  # NRMSE in percentage

# Extract coefficients for the regression equation
crop_coeffs <- round(coef(ML_crop_clean), 2)

crop_regression_eq <- paste0("logcropCd = ",
                              crop_coeffs["logsoilCd"], "*logsoilCd",
                              crop_coeffs["logSOC"], "*logSOC", crop_coeffs["logclay"], "*logclay", "\n",
                              "                  ",
                              crop_coeffs["pH"], "*pH+", 
                              ifelse("cropgrain" %in% names(crop_coeffs), crop_coeffs["cropgrain"], 0), "*grain+",
                              ifelse("cropstraw" %in% names(crop_coeffs), crop_coeffs["cropstraw"], 0), "*straw"
                            )

# Derive predictions based on the multiple linear regression
crop_data[crop == "straw", pred := crop_coeffs["logsoilCd"]*logsoilCd + crop_coeffs["logSOC"]*logSOC + crop_coeffs["logclay"]*logclay + 
                                   crop_coeffs["pH"]*pH + crop_coeffs["cropstraw"]]
crop_data[!crop == "straw",pred := crop_coeffs["logsoilCd"]*logsoilCd + crop_coeffs["logSOC"]*logSOC + crop_coeffs["logclay"]*logclay + 
                                   crop_coeffs["pH"]*pH + crop_coeffs["cropgrain"]] 
                    
```

### 1.1.1 Generate Extended Data Fig. 5

Below we illustrate the modeled results.

```{r plotting}
library(ggplot2); library(patchwork);library(ggsci)
#**Make plot**
# Combine metrics and equation for annotation
crop_annotation_text <- paste0(crop_regression_eq, "\n",
                              "R² = ", round(summary(ML_crop_clean)$r.squared, 2), "\n",
                              "NMAE = ", round(crop_nmae, 2), "\n",
                              "NRMSE = ", round(crop_nrmse, 2)
                              )

# Adjust annotation position for clarity
crop_annotate_x <- min(crop_data$logcropCd) - 1.5
crop_annotate_y <- 1.5


p1 <- ggplot(crop_data)+
      geom_point(aes(x = logcropCd, y = pred, color = crop, shape = source, alpha = outlier), size = 3) +  # Points
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed", linewidth = 1) +  # Line of perfect fit
      labs(
        x = "Measured log Crop Cd content",
        y = "Predicted log Crop Cd content",
        title = "(a)",
        color = "Crop",         # Custom title for color legend
        shape = "Data type",       # Custom title for shape legend
        alpha = "Data source"     # Custom title for alpha legend
      ) +
      xlim(c(-3.5, 1.5)) + ylim(c(-2.5, 1.5))+
      scale_color_npg()+
      scale_alpha_manual(values = c(0.3, 1))+
      scale_shape_manual(values = c(1, 16))+
      theme_minimal() +
      theme(
        text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5),
        legend.title = element_text(size = 12),    # Legend title font size
        legend.text = element_text(size = 10),     # Legend text font size
        legend.position = "bottom",        # Legend position
      ) +
      guides(
        alpha = guide_legend(override.aes = list(size = 2), nrow = 2),  # Adjust legend point size for alpha
        color = guide_legend(override.aes = list(size = 2), nrow = 2),  # Adjust legend point size for color
        shape = guide_legend(override.aes = list(size = 2), nrow = 2)   # Adjust legend point size for shape
      )+
      annotate(
        "text",
        x = crop_annotate_x,
        y = crop_annotate_y,
        label = crop_annotation_text,
        hjust = 0,
        vjust = 1,
        size = 3.5,
        color = "black"
      )

# Combine metrics and equation for annotation
solu_annotation_text <- paste0(solu_regression_eq, "\n",
                                "R² = ", round(summary(ML_solution_clean)$r.squared, 2), "\n",
                                "NMAE = ", round(solu_nmae, 2), "\n",
                                "NRMSE = ", round(solu_nrmse, 2)
                              )

# Adjust annotation position for clarity
solu_annotate_x <- min(soil_solution$logsolutionCd) - 0.1
solu_annotate_y <- 1.5

p2 <- ggplot(soil_solution)+
      geom_point(aes(x = logsolutionCd, y = pred, color = land_use, shape = source, alpha = outlier),size = 3) +  # Points
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed", linewidth = 1) +  # Line of perfect fit
      labs(
        x = "Measured log solution Cd content",
        y = "Predicted log solution Cd content",
        title = "(b)",
        color = "Land use",         # Custom title for color legend
        shape = "Data type",       # Custom title for shape legend
        alpha = "Data source"     # Custom title for alpha legend
      ) +
      xlim(c(-3.5, 1.5))+
      ylim(c(-2.5, 1.5))+
      scale_color_npg()+
      scale_alpha_manual(values = c(0.3, 1))+
      scale_shape_manual(values = c(1, 16))+
      theme_minimal() +
      theme(
        text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5),
        legend.title = element_text(size = 12),    # Legend title font size
        legend.text = element_text(size = 10),     # Legend text font size
        legend.position = "bottom",        # Legend position
      ) +
      guides(
        alpha = guide_legend(override.aes = list(size = 2), nrow = 2),  # Adjust legend point size for alpha
        color = guide_legend(override.aes = list(size = 2), nrow = 2),  # Adjust legend point size for color
        shape = guide_legend(override.aes = list(size = 2), nrow = 2)   # Adjust legend point size for shape
      )+
      annotate(
        "text",
        x = solu_annotate_x,
        y = solu_annotate_y,
        label = solu_annotation_text,
        hjust = 0,
        vjust = 1,
        size = 3.5,
        color = "black"
      )

# Combine p1 and p2 with a shared legend
combined_plot <- p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")  

combined_plot
# ggsave(combined_plot, filename = "Extended data/ED_Fig6.jpg",
#        width = 11,height = 5,units = "in",dpi = 300)

library(dplyr); library(tidyr)
crop_data_long <- crop_data %>% 
  dplyr::select(code, crop, source, outlier, pred, logcropCd)
  
solution_data_long <- soil_solution %>% 
  dplyr::select(code, land_use, source, outlier, pred, logsolutionCd)

library(openxlsx)
wb <- createWorkbook()

addWorksheet(wb, "panel_a")
writeData(wb, "panel_a", crop_data_long)

addWorksheet(wb, "panel_b")
writeData(wb, "panel_b", solution_data_long)

# saveWorkbook(
#   wb,
#   "Figure_Source_Data/SourceData_EDFig6.xlsx",
#   overwrite = TRUE
# )


```


## 1.2 Build Cd flux simulation model
```{r cars}
Cd_simulation <- function(cd_input, start_year = 1985) {

  ## -------- Checking input --------
  required_cols <- c(
    "Year", "soilCd", "SOC", "clay", "pH",
    "rice_yield", "straw_yield", "straw_recy",
    "dep", "irr", "fer", "man", "PS", "bulkdens"
  )

  missing_cols <- setdiff(required_cols, names(cd_input))
  if (length(missing_cols) > 0) {
    stop("Missing required columns: ",
         paste(missing_cols, collapse = ", "))
  }

  cd_input <- cd_input %>% arrange(Year)

  if (min(cd_input$Year) != start_year) {
    stop("cd_input must start from year ", start_year)
  }

  n <- nrow(cd_input)

  ## --------Initialize model output --------
  cd_input <- cd_input %>%
    mutate(
      Cd_solu  = NA_real_,         # Cd in soil solution, unit: μg/L 
      Cd_rice  = NA_real_,         # Cd in rice grain, unit: mg/kg
      Cd_straw = NA_real_,         # Cd in rice straw, unit: mg/kg
      crop     = NA_real_,         # net Cd removal (grain + removed straw), unit: g/ha
      res_in   = NA_real_,         # Cd crop residue input, unit: g/ha
      lea      = NA_real_,         # Cd leaching, unit: g/ha
      Cd_acc   = NA_real_          # soil Cd accumulation, unit: g/ha
    )

  ## -------- Loop for years --------
  for (i in seq_len(n)) {

    ini_soilCd <- cd_input$soilCd[i]

    logSOC  <- log10(cd_input$SOC[i])
    logclay <- log10(cd_input$clay[i])
    pH      <- cd_input$pH[i]

    ## --- Parameters derived based on regression model in section 1.1---
    Cd_rice <- 10^(crop_coeffs["logsoilCd"] * log10(ini_soilCd)
                   + crop_coeffs["logSOC"] * logSOC
                   + crop_coeffs["logclay"] * logclay
                   + crop_coeffs["pH"] * pH
                   + crop_coeffs["cropgrain"])
    
    Cd_straw <- 10^(crop_coeffs["logsoilCd"] * log10(ini_soilCd)
                   + crop_coeffs["logSOC"] * logSOC
                   + crop_coeffs["logclay"] * logclay
                   + crop_coeffs["pH"] * pH
                    + crop_coeffs["cropstraw"])

    ## --- Parameters derived based on regression model ---
    Cd_solu <- 10^(solu_coeffs["logsoilCd"] * log10(ini_soilCd)
                   + solu_coeffs["logSOC"] * logSOC
                   + solu_coeffs["logclay"] * logclay
                   + solu_coeffs["pH"] * pH
                   + solu_coeffs["land_usePaddy"])
    
    ## --- Cd output and soil accumulation ---
    res_in <- Cd_straw *
      cd_input$straw_yield[i] *
      cd_input$straw_recy[i]

    crop <- Cd_rice * cd_input$rice_yield[i] +
      Cd_straw * cd_input$straw_yield[i] *
      (1 - cd_input$straw_recy[i])

    lea <- Cd_solu * cd_input$PS[i] * 10

    Cd_acc <- cd_input$dep[i] +
      cd_input$irr[i] +
      cd_input$fer[i] +
      cd_input$man[i] -
      crop - lea

    ## --- write back ---
    cd_input$Cd_solu[i]  <- Cd_solu
    cd_input$Cd_rice[i]  <- Cd_rice
    cd_input$Cd_straw[i] <- Cd_straw
    cd_input$res_in[i]   <- res_in
    cd_input$crop[i]     <- crop
    cd_input$lea[i]      <- lea
    cd_input$Cd_acc[i]   <- Cd_acc

    ## --- soil Cd content update, stop in the last year---
    if (i < n){
      cd_input$soilCd[i + 1] <- ini_soilCd + Cd_acc / (10 * 0.2 * cd_input$bulkdens[i])
    }

  }

  return(cd_input)
}

```

## 1.3 Import input and run Cd model
```{r}
library(dplyr); library(tidyr)
all_Cd_input <- read.csv("model_data/historical_Cd_input.csv")

non_cal_site <- unique(filter(all_Cd_input, soil_type == "Non-calcareous")$ID)

Cd_output <- all_Cd_input %>%
  group_by(site) %>%
  group_modify(~ Cd_simulation(.x, start_year = 1985)) %>%
  ungroup()

## compare simulations with observations
all_obs <- read.csv("model_data/all_observation.csv")

all_sim <- Cd_output %>% 
  dplyr::select(ID, Year, soilCd, pH, SOC, soil_type) %>% 
  filter(Year %in% c(2014, 2019)) %>% 
  pivot_longer(
    cols = c(pH, SOC, soilCd),
    names_to = "Variable",
    values_to = "Simulation"
  ) 

all_sim$Year <- as.character(all_sim$Year)
all_obs$Year <- as.character(all_obs$Year)

comparison_all <- all_sim %>% 
  right_join(all_obs, 
             by = c("ID", "Year", "Variable")
               ) %>% 
  drop_na()

plot_df <- comparison_all %>% 
  filter(!is.na(value), !is.na(Simulation)) %>% 
  mutate(
    Variable = recode(
      Variable,
      soilCd = "Soil Cd",
      pH     = "pH",
      SOC    = "SOC"
    )
  ) %>% 
  filter(!(Variable == "pH" & soil_type == "Calcareous")) %>% 
  mutate(diff = abs(Simulation - value), 
         outlier = ifelse(diff>0.5 & Variable == "Soil Cd", 1, 0)) %>% 
  as.data.frame()

plot_df$Variable <- factor(plot_df$Variable, 
                           levels = c("Soil Cd", "SOC", "pH"))

metric_df <- plot_df %>% 
  group_by(Variable) %>% 
  reframe(
    NMAE  = mean(abs(Simulation - value)) /
            mean(abs(value)),
    NRMSE = sqrt(mean((Simulation - value)^2)) /
            mean(abs(value)),
    .groups = "drop"
  ) %>% 
  mutate(
    label = paste0(
      "NMAE = ", round(NMAE, 2), "\n",
      "NRMSE = ", round(NRMSE, 2)
    )
  )

```

### 1.3.1 generate Extended Data Fig. 1
```{r}
##**New plot merged**
p1 <- ggplot(plot_df %>% filter(Variable == "Soil Cd"), 
       aes(x = value, y = Simulation, color=Year, shape = factor(soil_type)))+
  geom_point()+
  scale_color_npg()+
  scale_shape_manual(name = "Soil type",
                     values = c(16, 17), 
                     breaks = c("Non-calcareous", "Calcareous"))+
  geom_abline(slope = 1, linetype = "dashed", color="red")+
  scale_x_continuous(limits = c(0, 1.5))+ 
  scale_y_continuous(limits = c(0, 1.5))+
  ggtitle("(a)")+
  xlab("Observation")+
  theme_bw()+
  theme(axis.ticks.length=unit(0.1, 'cm'),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        text = element_text(size = 12, family="serif"))+
  guides(fill = guide_legend(override.aes = list(shape = NA)))+
  annotate(
    "text",
    x = 1.25,
    y = 0.2,
    label = metric_df[metric_df$Variable == "Soil Cd", "label"],
    size = 3,
    color = "black"
  )

p2 <- ggplot(plot_df %>% filter(Variable == "SOC"), 
       aes(x = value, y = Simulation, color=Year, shape = factor(soil_type)))+
  geom_point()+
  scale_color_npg()+
  scale_shape_manual(name = "Soil type",
                     values = c(16, 17), 
                     breaks = c("Non-calcareous", "Calcareous"))+
  geom_abline(slope = 1, color="red")+
  ggtitle("(b)")+
  xlab("Observation")+
  scale_x_continuous(limits = c(0.5, 3.5))+
  scale_y_continuous(limits = c(0.5, 3.5))+
  theme_bw()+
  theme(axis.ticks.length=unit(0.1, 'cm'),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        text = element_text(size = 12, family="serif"))+
  guides(fill = guide_legend(override.aes = list(shape = NA)))+
  annotate(
    "text",
    x = 3,
    y = 0.8,
    label = metric_df[metric_df$Variable == "SOC", "label"],
    size = 3,
    color = "black"
  )

p3 <- ggplot(plot_df %>% filter(Variable == "pH"), 
       aes(x = value, y = Simulation, color=Year))+
  geom_point()+
  scale_color_npg()+
  geom_abline(slope = 1, color="red")+
  scale_x_continuous(limits = c(4, 7))+
  scale_y_continuous(limits = c(4, 7))+
  xlab("Observation")+
  ggtitle("(c)")+
  theme_bw()+
  theme(axis.ticks.length=unit(0.1, 'cm'),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        text = element_text(size = 12, family="serif"))+
  guides(fill = guide_legend(override.aes = list(shape = NA)))+
  annotate(
    "text",
    x = 6.5,
    y = 4.25,
    label = metric_df[metric_df$Variable == "pH", "label"],
    size = 3,
    color = "black"
  )

# Combine p1 and p2 with a shared legend
combined_plot <- p1 + p2 + p3 +
  plot_layout(guides = "collect") &  # Collect and share legends
  theme(legend.position = "bottom")  # Place the legend at the bottom

combined_plot

# # Save figure
# ggsave(combined_plot, filename = "Extended data/ED_Fig1.jpg",
#   width = 10,
#   height = 4.5,
#   units = "in",
#   dpi = 300
# )
# 
# ## Save figure source data
# write.csv(plot_df, "Figure_Source_Data/SourceData_EDFig1.csv", row.names = FALSE)
```

### 1.3.2 generate Figure 2 and legend
```{r pressure, echo=FALSE}
Cd_flux <- Cd_output %>% 
  dplyr::select(Year, dep, irr, fer, man, crop, lea, Cd_acc)

Cd_flux_summary <- Cd_output %>% 
  dplyr::select(Year, dep, irr, fer, man, crop, lea) %>% 
  group_by(Year) %>% summarise(across(everything(), list(mean = mean))) %>% 
      rename_all(~sub("_mean", "", .)) %>% as.data.frame() %>% 
  mutate(acc = dep + irr + man + fer - lea - crop)

Cd_flux_gather <- Cd_flux_summary %>% gather(item, amount, -c(Year)) %>% 
  mutate(source = ifelse(item %in% c("crop", "lea", "acc"), "Output", "Input"), 
         year_code=case_when(
                        Year %in% c(1985:1989) ~ 1,
                        Year %in% c(1990:1994) ~ 2, 
                        Year %in% c(1995:1999) ~ 3,
                        Year %in% c(2000:2004) ~ 4,
                        Year %in% c(2005:2009) ~ 5, 
                        Year %in% c(2010:2014) ~ 6,
                        Year %in% c(2015:2019) ~ 7))

Cd_flux_gather$item <- factor(Cd_flux_gather$item, 
                              levels = c("man", "fer", "irr", "dep", "lea", "crop", "acc"))

obs_soil_Cd <- all_obs %>% filter(Variable == "soilCd")
obs_soil_Cd$Year <- as.numeric(obs_soil_Cd$Year)

sim_Cd_group <- Cd_output %>% dplyr::select(ID, Year, soilCd, soil_type) %>% 
  group_by(Year) %>% na.omit() %>% 
  reframe(n=n(), simulation=c(mean(soilCd), quantile(soilCd, c(0.05, 0.5, 0.95))), 
            q = c("Mean value","5th percentile", "50th percentile", "95th percentile"))

sim_Cd_spread <- spread(sim_Cd_group, key = q, value = simulation)%>% 
  as.data.frame()

Cd_flux_gather_summary <- Cd_flux_gather %>% 
  group_by(source, item, year_code) %>% 
  reframe(amount = mean(amount)) %>% 
  as.data.frame()

Cd_flux_gather_summary$item <- factor(Cd_flux_gather_summary$item, 
                              levels = c("man", "fer", "irr", "dep", "lea", "crop", "acc"))

h1 <- ggplot()+
  geom_bar(data = filter(Cd_flux_gather_summary, source == "Input"),
           aes(year_code-0.2, y=amount, fill = item),
           stat='identity', color="black", width=0.3)+
  geom_bar(data = filter(Cd_flux_gather_summary, source == "Output"),
           aes(year_code+0.2, y=amount, fill = item),
           stat='identity', color="black", width=0.3)+
  ggtitle("(a)")+
  theme_bw()+
  theme(axis.ticks.length=unit(0.1, 'cm'), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"), 
        text = element_text(size = 14,family="serif"), 
        panel.spacing = unit(1.0, "lines"))+
  scale_fill_manual(name="Source/fate",                     
                    values = c('#DC0000B2','#F3D266', '#96C37D', 
                               '#8491B4B2', '#2F7FC1', '#91D1C2B2', 
                               '#C497B2',"#7E6148B2"),
                    breaks = c("man", "fer", "irr", "dep", "lea", "crop", "acc"), 
                    labels = c("Manure", "Fertilizer", "Irrigation", "Deposition", "Leaching", "Crop removal", "Accumulation"))+
  scale_y_continuous(limits = c(0, 28), breaks = c(0, 5, 10, 15, 20, 25))+
  scale_x_continuous(breaks = c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5),
                     labels = c("1985", "1990", "1995", 
                                "2000", "2005", "2010", "2015", "2020"))+
  ylab(expression(paste("Cadmium flux (g ha"^"-1", " yr"^"-1", ")",seq="")))+
  xlab("Year")

h2 <- ggplot(data=sim_Cd_spread, aes(x=Year, y=`Mean value`))+
  geom_boxplot(data=obs_soil_Cd,
               mapping=aes(Year, value, group=Year, fill=factor(Year)),
               width=1.0)+
  stat_summary(data=obs_soil_Cd, mapping=aes(Year, value, group=Year),
               fun = "mean", geom = "point", shape = 24,
               size = 2, fill = "red")+
  geom_line(color = "red",linewidth=1.0)+  
  geom_ribbon(aes(ymin = `5th percentile`, ymax = `95th percentile`), 
              alpha = 0.1)+
  scale_color_lancet(name="Simulation")+
  scale_fill_manual(name="Observation", values=c("darkorange", "yellow"))+
  scale_x_continuous(limits=c(1984, 2020), 
                     breaks = c(1985, 1990, 1995, 2000, 2005, 2010, 2015, 2020),
                     labels = c("1985", "1990", "1995", 
                                "2000", "2005", "2010", "2015", "2020"))+
  ylab(expression(paste("Soil total Cd content (mg kg"^"-1", ")",seq="")))+
  xlab("Year")+
  ggtitle("(b)")+
  theme_bw()+
  theme(axis.ticks.length=unit(0.2, 'cm'),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"), 
        text = element_text(size = 14,family="serif"),
        plot.margin = unit(c(0,2,0,0), "lines"))

library(cowplot)
legend_h1 <- get_legend(h1)
legend_h2 <- get_legend(h2)

legend_plot <- (as_ggplot(legend_h1))/(as_ggplot(legend_h2))

legend_plot

com_Cd_sim <- (h1+theme(legend.position = "none"))|(h2+theme(legend.position = "none"))

com_Cd_sim

# # Save figure and legend
# ggsave("Figures/Fig2.pdf", com_Cd_sim,
#        width = 8.5,
#        height = 4,
#        device = cairo_pdf)
# 
# ggsave("Figures/Fig2_legend.pdf", legend_plot,
#        width = 4,
#        height = 4,
#        device = cairo_pdf)

## Save Figure source data
library(openxlsx)
wb <- createWorkbook()

addWorksheet(wb, "panel_a")
writeData(wb, "panel_a", Cd_flux_gather_summary)

addWorksheet(wb, "panel_b_simulation")
writeData(wb, "panel_b_simulation", sim_Cd_spread)

addWorksheet(wb, "panel_b_observation")
writeData(
  wb,
  "panel_b_observation",
  obs_soil_Cd %>% drop_na()
)

# saveWorkbook(
#   wb,
#   "Figure_Source_Data/SourceData_Fig2.xlsx",
#   overwrite = TRUE
# )
```

## 1.5 Calculate critical input
```{r}
crit_Cd_noncal <- Cd_output %>% 
  filter(Year == 2019) %>%      # use the value in the last year
  mutate(crit_pH_Cd = (log10(0.23) - crop_coeffs["logsoilCd"]*log10(soilCd) - crop_coeffs["logSOC"]*log10(SOC) - crop_coeffs["logclay"]*log10(clay) - crop_coeffs["cropgrain"])/crop_coeffs["pH"],
         crit_pH = ifelse(crit_pH_Cd < 5.5, 5.5, crit_pH_Cd),
         new_riceCd = 10^(crop_coeffs["logsoilCd"]*log10(soilCd) + crop_coeffs["pH"]*crit_pH + crop_coeffs["logSOC"]*log10(SOC) + crop_coeffs["logclay"]*log10(clay) + crop_coeffs["cropgrain"]),
         crit_riceCd = 0.23,
         crit_soilCd = 10^( (log10(crit_riceCd) - (+ crop_coeffs["cropgrain"] + crop_coeffs["logSOC"]*log10(SOC) + crop_coeffs["logclay"]*log10(clay) + crop_coeffs["pH"]* crit_pH))/crop_coeffs["logsoilCd"]),
         crit_soluCd = 10^(solu_coeffs["logsoilCd"] * log10(crit_soilCd) + solu_coeffs["logSOC"]*log10(SOC) + solu_coeffs["logclay"]*log10(clay) + solu_coeffs["pH"]*crit_pH + solu_coeffs["land_usePaddy"]),
         crit_Cd_rice = crit_riceCd * rice_yield, 
         crit_Cd_upt = crit_Cd_rice,
         crit_Cd_lea = crit_soluCd * PS * 10, 
         crit_Cdin = crit_Cd_rice + crit_Cd_lea,  
         cur_Cd_in = dep + irr + fer + man)

# Get critical Cd input
crit_Cd_in <- crit_Cd_noncal %>% 
  mutate(tot_in = crit_Cd_rice + crit_Cd_lea, 
         crit_in = crit_Cd_rice + crit_Cd_lea,
         scenario = "Critical input") %>%
  dplyr::select(ID, scenario, soil_type, tot_in, crit_in) %>%
  arrange(ID)

# Get critical soil pH, soil Cd content and soil solution Cd content
crit_range <- crit_Cd_noncal %>% 
  dplyr::select(ID, soil_type, crit_pH, crit_soilCd, crit_soluCd) %>% 
  gather(item, value, -c(ID, soil_type))

crit_range$soil_type <- factor(crit_range$soil_type, 
                               levels = c("Non-calcareous", "Calcareous"))

crit_Cd_gather <- crit_range %>% 
  mutate(scenario = "Critical value", 
         item = case_when(item == "crit_pH"~"pH", 
                          item == "crit_soilCd"~"soilCd", 
                          item == "crit_soluCd"~"Cd_solu")) %>% 
  dplyr::select(-ID)

crit_range$item <- factor(crit_range$item, 
                          levels = c("crit_pH", "crit_soilCd", "crit_soluCd"), 
                          labels = c("Critical pH", 
                                     "Critical soil total Cd", 
                                     "Critical soil solution Cd"))
```
### 1.5.1 Generate Extended Data Fig. 5
```{r}
panel_labels <- data.frame(
  item = levels(crit_range$item),
  label = c("(a)", "(b)", "(c)")
)

ggplot(data = crit_range)+
  geom_boxplot(aes(x = soil_type, y = value, fill = soil_type), width = 0.5)+ 
  stat_summary(aes(x = soil_type, y = value), fun = "mean", 
    geom = "point", shape = 23, size = 3)+
  facet_wrap(~item, scales = "free_y", switch = 'y')+
  geom_text(
    data = panel_labels,
    aes(x = -Inf, y = Inf, label = label),
    hjust = -0.2, vjust = 1.2,
    inherit.aes = FALSE,
    size = 5,
    family = "serif"
  ) +
  xlab("")+
  ylab("")+
  scale_fill_npg()+
  theme_bw()+
  theme(axis.ticks.length=unit(0.1, 'cm'), legend.position = "none", 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"), 
        text = element_text(size = 14, family="serif"),
        panel.spacing = unit(1.0, "lines"))+
  theme(strip.placement = "outside") +
  theme(axis.title.y = element_blank(),
        strip.background = element_blank())

# ggsave(filename = "Extended data/ED_Fig5.jpg",
#   width = 9,
#   height = 4,
#   units = "in",
#   dpi = 300
# )
# 
# write.csv(crit_range, "Figure_Source_Data/SourceData_EDFig5.csv", 
#           row.names = FALSE,
#           fileEncoding = "UTF-8")

```

# 2. Scenario analysis
## 2.1 Modelling results for scenarios BAU, BNP, BNPR and BNPL
```{r}
scenario_Cd_input <- read.csv("model_data/scenario_input_with_lime.csv")

past_Cd_input <- all_Cd_input %>% 
  mutate(site = ID, scenario = "Past", lime = 0)

all_scenario_input <- scenario_Cd_input %>% 
  bind_rows(past_Cd_input)

BAU_Cd_output <- all_scenario_input %>%
  filter(scenario %in% c("BAU", "Past")) %>% 
  group_by(site) %>%
  group_modify(~ Cd_simulation(.x, start_year = 1985)) %>%
  ungroup()

BNP_Cd_output <- all_scenario_input %>%
  filter(scenario %in% c("BNP", "Past")) %>% 
  group_by(site) %>%
  group_modify(~ Cd_simulation(.x, start_year = 1985)) %>%
  ungroup()

BNPR_Cd_output <- all_scenario_input %>%
  filter(scenario %in% c("BNPR", "Past")) %>% 
  group_by(site) %>%
  group_modify(~ Cd_simulation(.x, start_year = 1985)) %>%
  ungroup()

BNPL_Cd_output <- all_scenario_input %>%
  filter(scenario %in% c("BNPL", "Past")) %>% 
  group_by(site) %>%
  group_modify(~ Cd_simulation(.x, start_year = 1985)) %>%
  ungroup()

BNPRL_Cd_output <- all_scenario_input %>%
  filter(scenario %in% c("BNPRLopt", "Past")) %>% 
  group_by(site) %>%
  group_modify(~ Cd_simulation(.x, start_year = 1985)) %>%
  ungroup()

OPT_Cd_output <- all_scenario_input %>%
  filter(scenario %in% c("BNPRLopt(dep)", "Past")) %>% 
  group_by(site) %>%
  group_modify(~ Cd_simulation(.x, start_year = 1985)) %>%
  ungroup()

```

## 2.2 Effects of soil properties on Cd concentration and Cd leaching in BAU scenario
```{r}
BAU_Cd_leaching <- BAU_Cd_output %>% 
  dplyr::select(ID, clay, SOC, pH, Cd_solu, lea) %>% 
  mutate(soc_level = case_when(SOC<0.5~"Very low (<0.5%)", 
                               SOC<1.5~"Low (0.5~1.5%)",
                               SOC<2.5~"Medium (1.5~2.5%)",
                               TRUE~"High (>2.5%)"), 
         clay_level = case_when(clay<18~"Sandy (<18%)", 
                                clay<35~"Loamy (18-35%)", 
                                TRUE~"Clay (>35%)"))

BAU_Cd_leaching$soc_level <- factor(BAU_Cd_leaching$soc_level, 
                                    levels = c("High (>2.5%)", 
                                               "Medium (1.5~2.5%)", 
                                               "Low (0.5~1.5%)", 
                                              "Very low (<0.5%)" 
                                               ))

BAU_Cd_leaching$clay_level <- factor(BAU_Cd_leaching$clay_level, 
                                    levels = c("Clay (>35%)", 
                                               "Loamy (18-35%)", 
                                               "Sandy (<18%)" 
                                               ))
```

###2.2.1 generate Extended Data Fig. 2
```{r}
h1 <- ggplot(data = BAU_Cd_leaching)+
  geom_point(aes(x = pH, y = Cd_solu, color = soc_level, alpha = clay_level))+
  xlim(c(4.3, 7))+
  ylim(c(0, 5))+
  scale_color_npg()+                  
  labs(
    title = "(a)",
    y = "Cadmium in soil solution (µg/L)",
    color = "SOC",
    alpha = "Clay"
  ) +
  ylab(expression(paste("Cadmium in soil solution (µg L"^"-1", ")",seq="")))+
  theme_bw()+
  theme(text = element_text(size = 12, family="serif"))

h2 <- ggplot(data = BAU_Cd_leaching)+
  geom_point(aes(x = pH, y = lea, color = soc_level, alpha = clay_level))+
  xlim(c(4.3, 7))+
  ylim(c(0, 50))+
  scale_color_npg()+                  
  labs(
    title = "(b)",
    y = "Cadmium leaching rate (g/ha/yr)",
    color = "SOC",
    alpha = "Clay"
  ) +
  ylab(expression(paste("Cadmium leaching rate (g ha"^"-1", " yr"^"-1" ,")",seq="")))+
  theme_bw()+
  theme(text = element_text(size = 12, family="serif"))

# Combine p1 and p2 with a shared legend
BAU_leaching <- h1 + h2 + 
  plot_layout(guides = "collect") &  # Collect and share legends
  theme(legend.position = "right")  # Place the legend at the bottom

BAU_leaching

# ggsave(filename = "Extended data/ED_Fig2.jpg",
#   width = 10,           
#   height = 4.5,          
#   units = "in",        
#   dpi = 300    
# )
# 
# write.csv(BAU_Cd_leaching, 
#           "Figure_Source_Data/SourceData_EDFig2.csv", row.names = FALSE)
```
## 2.3 Total and critical cadmium inputs across scenarios and sites
```{r}
all_scenario_cdin <- all_scenario_input %>% 
  filter(Year == 2020) %>% 
  plyr::rbind.fill(crit_Cd_in) %>%
  dplyr::select(ID, scenario, soil_type, dep, man, irr, fer, tot_in, crit_in) %>%
  mutate(tot_in = ifelse(scenario == "Critical input", crit_in, dep + man + irr + fer)) %>% 
  gather(variable, value, -c(ID, scenario, soil_type)) %>% 
  filter(!ID %in% unique(plot_df[plot_df$outlier==1, "ID"])) %>% 
  filter(complete.cases(.)) 

all_scenario_cdin$variable <- factor(all_scenario_cdin$variable,
                                     levels = c("dep", "man", "irr", "fer", "tot_in", "crit_in"),
                                     labels = c("deposition", "manure", "irrigation", "fertilizer", 
                                                "total input", "critical input"))
# generate Extended Data Fig.3
ggplot(data = all_scenario_cdin %>% 
         filter(variable == "total input") %>% 
         filter(!scenario %in% c("Past", "BNPL", "BNPRLopt(dep)"))
       )+
  geom_violin(aes(x = scenario, y = value, fill = scenario))+
  stat_summary(aes(x = scenario, y = value), fun = "mean", 
    geom = "point", shape = 18, size = 2)+
  scale_fill_npg(name = "Scenario")+
  facet_grid(cols = vars(soil_type))+
  xlab("Scenario")+
  ylab(expression(paste("Cadmium input (g ha"^"-1", " yr"^"-1" ,")",seq="")))+
  theme_bw()+
  theme(text = element_text(size = 14, family="serif"), 
        legend.position = "none")

# ggsave(filename = "Extended data/ED_Fig3.jpg",
#        width = 10,           
#        height = 5,          
#        units = "in",         
#        dpi = 300           
#        )
# 
# write.csv(all_scenario_cdin %>% arrange(ID), 
#           "Figure_Source_Data/SourceData_EDFig3.csv", row.names = FALSE)

```

## 2.3 Scenario effects on manure recycling and cadmium deposition
```{r}
scenario_dep_man <- all_scenario_input %>% filter(Year == 2020)

manure_compare <- scenario_dep_man %>% 
  filter(!ID %in% unique(plot_df[plot_df$outlier==1, "ID"])) %>% 
  dplyr::select(ID, man, soil_type, scenario) %>% 
  filter(!scenario %in% c("Past", "BNPL")) %>% 
  arrange(ID)

manure_compare$scenario <- factor(manure_compare$scenario, 
                                  levels = c( "BAU", "BNP", 
                                              "BNPRLopt","BNPRLopt(dep)", "BNPR"))

mean_manure <- manure_compare %>% 
  group_by(scenario) %>% 
  reframe(mean_manure = mean(man)/0.67) %>%     # mean manure Cd at 0.67 mg/kg
  mutate(ratio = mean_manure/max(mean_manure))

# generate Extended Data Fig.4
h1 <- ggplot(data = mean_manure)+
  geom_bar(aes(x = scenario, y = ratio, fill = scenario),
           color = "black", stat = "identity", position="stack", width=0.4)+
  scale_fill_npg(name = "Scenario")+
  scale_y_continuous(labels = scales::percent)+
  xlab("")+
  ylab(expression(paste("Manure recycling ratio (%)",seq="")))+
  theme_bw()+
  theme(text = element_text(size = 10, family="serif"), 
        legend.position = "none")

h2 <- ggplot(manure_compare, 
       aes(x = man/0.67, color=factor(scenario)))+
  stat_ecdf()+
  scale_y_continuous(labels = scales::percent)+
  scale_color_npg(name="Scenario")+
  ggtitle("(a)")+
  xlab(expression(paste("Manure dose (tons ha"^"-1", ")",seq="")))+
  ylab("Cumulative frequency") +
  theme_bw()+
  theme(axis.ticks.length=unit(0.1, 'cm'),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = 0.5),  
        legend.position = "bottom", 
        text = element_text(size = 14,family="serif"), 
        plot.margin = unit(c(0.1, 0, 0.1, 0.1), "cm"))

library(ggpubr)
grob_h1 <- ggplotGrob(h1)

# Overlay h1 in the blank space of h2
comb_plot_man <- h2 + 
  annotation_custom(grob = grob_h1, 
                    xmin = 3.65, xmax = 11.95,  # Adjust placement based on your data
                    ymin = -0.05, ymax = 0.6)  # Adjust placement based on your data

comb_plot_man

dep_compare <- scenario_dep_man %>% 
  filter(!ID %in% unique(plot_df[plot_df$outlier==1, "ID"])) %>% 
  dplyr::select(ID, dep, soil_type, scenario) %>% 
  filter(!scenario %in% c("Past", "BNPL"))%>% 
  arrange(ID)

dep_compare$scenario <- factor(dep_compare$scenario, 
                                  levels = c("BAU", "BNP", 
                                             "BNPRLopt","BNPRLopt(dep)", "BNPR"))

mean_dep <- dep_compare %>% 
  group_by(scenario) %>% 
  reframe(mean_dep = mean(dep)) %>% 
  mutate(ratio = mean_dep/max(mean_dep))

h1 <- ggplot(data = mean_dep)+
  geom_bar(aes(x = scenario, y = ratio, fill = scenario),
           color = "black", stat = "identity", position="stack", width=0.4)+
  scale_fill_npg(name = "Scenario")+
  scale_y_continuous(labels = scales::percent)+
  xlab("")+
  ylab(expression(paste("Ratio to current deposition rate (%)",seq="")))+
  theme_bw()+
  theme(text = element_text(size = 10, family="serif"), 
        legend.position = "none")

h2 <- ggplot(dep_compare, 
       aes(x = dep, color=factor(scenario)))+
  stat_ecdf()+
  scale_y_continuous(labels = scales::percent)+
  scale_color_npg(name="Scenario")+
  xlab(expression(paste("Cd deposition rate (g ha"^"-1", ")",seq="")))+
  ggtitle("(b)")+
  ylab("") +
  theme_bw()+
  theme(axis.ticks.length=unit(0.1, 'cm'),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = 0.5),  
        legend.position = "bottom", 
        text = element_text(size = 14,family="serif"), 
        plot.margin = unit(c(0.1, 0.1, 0.1, 0), "cm"))

grob_h1 <- ggplotGrob(h1)

# Overlay h1 in the blank space of h2
comb_plot_dep <- h2 + 
  annotation_custom(grob = grob_h1, 
                    xmin =6, xmax = 20,  # Adjust placement based on your data
                    ymin = -0.05, ymax = 0.6)  # Adjust placement based on your data

comb_plot_dep 

library(lemon)
com_plot <- grid_arrange_shared_legend(comb_plot_man, comb_plot_dep, ncol=2, 
                                       position="bottom")

plot(com_plot) 

# ggsave(com_plot, filename = "Extended data/ED_Fig4.jpg",,
#   width = 13.5,
#   height = 6,
#   units = "in",
#   dpi = 300
# )

wb = createWorkbook()

addWorksheet(wb, "manure_dose")
writeData(wb, "manure_dose", manure_compare)

addWorksheet(wb, "manure_recycling_ratio")
writeData(wb, "manure_recycling_ratio", mean_manure)

addWorksheet(wb, "Cd_deposition")
writeData(
  wb,
  "Cd_deposition",
  dep_compare
)

addWorksheet(wb, "ratio_to_current_deposition")
writeData(
  wb,
  "ratio_to_current_deposition",
  mean_dep
)

# saveWorkbook(
#   wb,
#   "Figure_Source_Data/SourceData_EDFig4.xlsx",
#   overwrite = TRUE
# )
```

## 2.4 Effects of management scenarios on cadmium inputs and outputs
```{r}
Cd_scenario_output <- rbind(BAU_Cd_output, BNP_Cd_output, BNPR_Cd_output,
                            BNPL_Cd_output, BNPRL_Cd_output)%>% 
  filter(!ID %in% unique(plot_df[plot_df$outlier==1, "ID"]))

Cd_scenario_flux_summary <- Cd_scenario_output %>% 
  dplyr::select(Year, dep, irr, fer, man, crop, lea, scenario, soil_type) %>% 
  mutate(scenario = ifelse(Year<2020, "Past", scenario)) %>% 
  group_by(scenario, soil_type) %>% 
  reframe(across(everything(), list(mean = mean))) %>% 
      rename_all(~sub("_mean", "", .)) %>% as.data.frame() %>% 
  mutate(acc = dep + irr + man + fer - lea - crop)

Cd_scenario_flux_gather <- Cd_scenario_flux_summary %>% 
  dplyr::select(-Year) %>% 
  gather(source, amount, -c(scenario, soil_type)) %>% 
  mutate(flux = ifelse(source %in% c("crop", "lea", "acc"), "Output", "Input"), 
         x = case_when(scenario == "Past"~1, 
                       scenario == "BAU"~2,
                       scenario == "BNP"~3,
                       scenario == "BNPR"~4,
                       scenario == "BNPL"~5, 
                       scenario == "BNPRLopt"~6))

Cd_scenario_flux_gather$source <- factor(Cd_scenario_flux_gather$source, 
                              levels = c("man", "fer",  "irr","dep", "lea", "crop", "acc"))

crit_Cd_cal <- mean(crit_Cd_in[crit_Cd_in$soil_type =="Calcareous", ]$crit_in)
crit_Cd_non_cal <- mean(crit_Cd_in[crit_Cd_in$soil_type !="Calcareous",]$crit_in)

# Generate Figure 3
h1 <- ggplot()+
  geom_bar(data=filter(Cd_scenario_flux_gather %>% 
                         filter(soil_type == "Non-calcareous"), flux=="Input"), 
                   aes(x, amount, fill=source), color="black",
                   stat='identity', width = 0.3)+
  geom_bar(data=filter(Cd_scenario_flux_gather %>% 
                         filter(soil_type == "Non-calcareous"), flux=="Output"), 
                   aes(x+0.4, amount, fill=source), color="black",
                   stat='identity', width = 0.3)+
  geom_hline(yintercept = crit_Cd_cal, 
             linetype = 2,
              color="black")+
  scale_fill_manual(values = c('#DC0000B2','#F3D266', '#96C37D', 
                               '#8491B4B2', '#2F7FC1', '#91D1C2B2', 
                               '#C497B2'),
                    breaks = c("man", "fer", "irr","dep", "lea", "crop", "acc"), 
                    labels = c("Manure", "Fertilizer", "Irrigation", 
                               "Deposition"~~~~~~~~~~~~"", 
                               "Leaching", "Crop removal", "Accumulation"))+
  labs(x="", y = "Cd input/output (g/ha/yr)", 
       fill=expression("Cadmium Input"~~~~~~~"Cadmium Output"))+
  ylab(expression(paste("Cadmium flux (g ha"^"-1", " yr"^"-1", ")",seq="")))+
  scale_x_continuous(breaks = c(1.25, 2.25,3.25, 4.25, 5.25, 6.25),
                     labels = c("Past","BAU", "BNP","BNPR", "BNPL", "BNPRLopt"))+
  scale_y_continuous(limits = c(-5, 16))+
  guides(fill = guide_legend(ncol = 2))+
  geom_hline(yintercept = 0, color = "black") +
  ggtitle("(a)")+
  theme_bw()+
  theme(legend.direction = "vertical", legend.box = "horizontal", 
        axis.ticks.length=unit(0.2, 'cm'), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"), 
        text = element_text(size = 14, family="serif"),
        plot.margin = unit(c(0,0,0,0), "lines"))

h2 <- ggplot()+
  geom_bar(data=filter(Cd_scenario_flux_gather %>% 
                         filter(soil_type != "Non-calcareous"), flux=="Input"), 
                   aes(x, amount, fill=source), color="black",
                   stat='identity', width = 0.3)+
  geom_bar(data=filter(Cd_scenario_flux_gather %>% 
                         filter(soil_type != "Non-calcareous"), flux=="Output"), 
                   aes(x+0.4, amount, fill=source), color="black",
                   stat='identity', width = 0.3)+
  geom_hline(yintercept = crit_Cd_non_cal, 
             linetype = 2,
              color="black")+
  scale_y_continuous(limits = c(-5, 16))+
  scale_fill_manual(values = c('#DC0000B2','#F3D266', '#96C37D', 
                               '#8491B4B2', '#2F7FC1', '#91D1C2B2', 
                               '#C497B2'),
                    breaks = c("man", "fer", "irr","dep", "lea", "crop", "acc"), 
                    labels = c("Manure", "Fertilizer", "Irrigation", 
                               "Deposition"~~~~~~~~~~~~"", 
                               "Leaching", "Crop removal", "Accumulation"))+
  labs(x="", y = "", 
       fill=expression("Cadmium Input"~~~~~~~~"Cadmium Output"))+
  scale_x_continuous(breaks = c(1.25, 2.25,3.25, 4.25, 5.25, 6.25),
                     labels = c("Past","BAU", "BNP","BNPR", "BNPL", "BNPRLopt"))+
  guides(fill = guide_legend(ncol = 2))+
  geom_hline(yintercept = 0, color = "black") +
  ggtitle("(b)")+
  theme_bw()+
  theme(legend.direction = "vertical", legend.box = "horizontal",
        axis.ticks.length=unit(0.2, 'cm'), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"), 
        text = element_text(size = 14, family="serif"),
        plot.margin = unit(c(0,0,0,0), "lines"))

legend_h1 <- get_legend(h1)

legend_plot <- as_ggplot(legend_h1)

legend_plot

combined_plot <- (h1+theme(legend.position = "none"))|(h2+theme(legend.position = "none"))
combined_plot

# ggsave("Figures/Fig3.pdf", combined_plot,
#        width = 10,
#        height = 5,
#        device = cairo_pdf)
# 
# ggsave("Figures/Fig3_legend.pdf", legend_plot,
#        width = 3.5, height = 3,
#        device = cairo_pdf)
# 
# write.csv(Cd_scenario_flux_gather,
#           "Figure_Source_Data/SourceData_Fig3.csv", row.names = FALSE)
```

## 2.5 Impacts of management on soil pH and cadmium concentrations in soils and rice grain
```{r}
scenario_summary <- Cd_scenario_output %>%
  dplyr::select(ID, Year, pH, soilCd, Cd_rice, soil_type, scenario) %>% 
  # filter(Year>=2020) %>% 
  group_by(Year, scenario, soil_type) %>% 
  reframe(
    mean_pH = mean(pH),
    lower_pH = min(pH),
    upper_pH = max(pH), 
    mean_soilCd = mean(soilCd),
    lower_soilCd = min(soilCd),
    upper_soilCd = max(soilCd), 
    mean_riceCd = mean(Cd_rice),
    lower_riceCd = min(Cd_rice),
    upper_riceCd = max(Cd_rice)
  ) %>%
  ungroup()

past_summary <- scenario_summary %>% 
  filter(scenario == "Past")

add_past_scenario <- past_summary %>% 
  mutate(scenario = "BAU") %>% 
  bind_rows(past_summary %>% mutate(scenario = "BNP"))%>% 
  bind_rows(past_summary %>% mutate(scenario = "BNPR"))%>% 
  bind_rows(past_summary %>% mutate(scenario = "BNPL"))%>% 
  bind_rows(past_summary %>% mutate(scenario = "BNPRLopt"))


summary_riceCd <- scenario_summary %>% 
  filter(scenario != "Past") %>% 
  bind_rows(add_past_scenario)


summary_riceCd$scenario <- factor(summary_riceCd$scenario, 
                                  levels = c("BAU", "BNP", "BNPR", "BNPL", "BNPRLopt"))

summary_riceCd$soil_type <- factor(summary_riceCd$soil_type, 
                                  levels = c("Non-calcareous", "Calcareous"))

# generate Figure 4
h1 <- ggplot(summary_riceCd, 
             aes(x = Year, y = mean_pH, color = soil_type)) +
  geom_line(size = 1) +                        
  geom_ribbon(aes(ymin = lower_pH, ymax = upper_pH, fill = soil_type), 
              alpha = 0.2, color = NA) +
  xlab("")+
  scale_color_npg()+
  scale_fill_npg()+
  geom_abline(slope = 0, intercept = 0.2, color= "red")+
  facet_wrap(~scenario, ncol = 5) +                    
  labs(
    title = "(a)",
    y = "pH",
    color = "Scenario",
    fill = "Soil type"
  ) +
  theme_bw()+
  theme(text = element_text(size = 14, family="serif"), legend.position = "none")

h2 <- ggplot(summary_riceCd, 
             aes(x = Year, y = mean_soilCd, color = soil_type)) +
  geom_line(size = 1) +                         
  geom_ribbon(aes(ymin = lower_soilCd, ymax = upper_soilCd, fill = soil_type), 
              alpha = 0.2, color = NA) +   
  xlab("")+
  scale_color_npg()+
  scale_fill_npg()+
  facet_wrap(~scenario, ncol = 5) +                     
  labs(
     title = "(b)",
    y = "Soil Cd Content (mg/kg)",
    color = "Scenario",
    fill = "Soil type"
  ) +
  ylab(expression(paste("Soil Cd content (mg kg"^"-1", ")",seq="")))+
  theme_bw()+
  theme(text = element_text(size = 14, family="serif"), legend.position = "none")    

h3 <- ggplot(summary_riceCd, 
             aes(x = Year, y = mean_riceCd, color = soil_type)) +
  geom_line(size = 1) +                      
  geom_ribbon(aes(ymin = lower_riceCd, ymax = upper_riceCd, fill = soil_type), 
              alpha = 0.2, color = NA) + 
  scale_color_npg()+
  scale_fill_npg()+
  geom_abline(slope = 0, intercept = 0.23, color= "red", 
              linetype = "dashed", linewidth = 0.5)+
  facet_wrap(~scenario, ncol = 5) +                    
  labs(
     title = "(c)",
    y = "Rice Cd Content (mg/kg)",
    color = "Scenario",
    fill = "Soil type"
  ) +
  ylab(expression(paste("Rice Cd content (mg kg"^"-1", ")",seq="")))+
  theme_bw()+
  theme(text = element_text(size = 14, family="serif"))

# Combine p1 and p2 with a shared legend
combined_plot <- h1 + h2 + h3 +
  plot_layout(guides = "collect", nrow = 3) &  # Collect and share legends
  theme(legend.position = "bottom")  # Place the legend at the bottom
combined_plot 

# ggsave("Figures/Figure_4.pdf", combined_plot,
#        width = 10,
#        height = 8,
#        device = cairo_pdf)
# 
# write.csv(summary_riceCd,
#           "Figure_Source_Data/SourceData_Fig4.csv", row.names = FALSE)
```

# 3. Spatial analysis
## 3.1 Spatial variation in cadmium inputs by manure and deposition under different management scenarios
```{r}
library(sf)
library(raster)
library(stars)
library(gstat)

QY_rast <- read_stars("spatial_data/rice_cover.tiff") 

manure_Cd_sf <- st_read("spatial_data/spatial_manure_Cd.shp")

QYBorder <- read_sf("spatial_data/Qiyang_county.shp") 

idw_1 <- idw(formula = BNPR ~ 1,
             locations = manure_Cd_sf,
             newdata = QY_rast,
             idp = 5) %>%
  as.data.frame() %>% dplyr::select(c(1:3)) %>%
  drop_na() %>%
  mutate(scenario = "BNPR")

idw_2 <- idw(formula = BNPRLopt1 ~ 1,
             locations = manure_Cd_sf,
             newdata = QY_rast,
             idp =5) %>%
  as.data.frame() %>% dplyr::select(c(1:3)) %>%
  drop_na() %>%
  mutate(scenario = "BNPRLopt")

idw_3 <- idw(formula = BNPRLopt2 ~ 1,
             locations = manure_Cd_sf,
             newdata = QY_rast,
             idp = 5) %>%
  as.data.frame() %>% dplyr::select(c(1:3)) %>%
  drop_na() %>%
  mutate(scenario = "BNPRLopt(dep)")

idw_manureCd <- rbind(idw_1, idw_2, idw_3) %>%
  mutate(range = case_when(var1.pred>3 ~ ">3",
                           var1.pred<=3 & var1.pred>2 ~  "2-3",
                           var1.pred<=2 & var1.pred>1 ~ "1-2",
                           var1.pred<=1 & var1.pred>0.5 ~ "0-1",
                           var1.pred<=0.5~ "0"))

idw_manureCd$range <- factor(idw_manureCd$range,
                         levels = c(">3", "2-3", "1-2", "0-1", "0"))

idw_manureCd$scenario <- factor(idw_manureCd$scenario,
                         levels = c("BAU", "BNP", "BNPR", "BNPRLopt", "BNPRLopt(dep)"))

idw_manure_spread <- idw_manureCd[, -5] %>% 
  spread(key = scenario, value = var1.pred)

## generate Figure 5a
plot_man <- ggplot()+
  geom_raster(data=idw_manureCd, aes(x=x, y=y, fill=range))+
  geom_sf(data = QYBorder, color="black")+
  scale_fill_locuszoom(name = "Manure Cd input")+
  facet_wrap(~scenario)+
  labs(title ="(a)")+
  theme_void()+
  theme(plot.title = element_text(hjust = 0),
        text = element_text(size = 16, family="serif"))+
  coord_sf(crs=st_crs(QY_rast))


## generate Figure 5b
deposition_Cd_sf <- st_read("spatial_data/spatial_deposition_Cd.shp")

idw_4 <- idw(formula = BNPR ~ 1,
             locations = deposition_Cd_sf,
             newdata = QY_rast,
             idp = 5) %>%
  as.data.frame() %>% dplyr::select(c(1:3)) %>%
  drop_na() %>%
  mutate(scenario = "BNPR")

idw_5 <- idw(formula = BNPRLopt1 ~ 1,
             locations = deposition_Cd_sf,
             newdata = QY_rast,
             idp = 5) %>%
  as.data.frame() %>% dplyr::select(c(1:3)) %>%
  drop_na() %>%
  mutate(scenario = "BNPRLopt")

idw_6 <- idw(formula = BNPRLopt2 ~ 1,
             locations = deposition_Cd_sf,
             newdata = QY_rast,
             idp = 5) %>%
  as.data.frame() %>% dplyr::select(c(1:3)) %>%
  drop_na() %>%
  mutate(scenario = "BNPRLopt(dep)")
 
idw_depCd <- rbind(idw_4, idw_5, idw_6) %>%
  mutate(range = case_when(var1.pred>6 ~ ">6",
                           var1.pred<=6 & var1.pred>4 ~  "4-6",
                           var1.pred<=4 & var1.pred>2 ~ "2-4",
                           var1.pred<=2 & var1.pred>1 ~ "0-2",
                           var1.pred<=1~ "0"))

idw_depCd$range <- factor(idw_depCd$range,
                         levels = c(">6", "4-6", "2-4", "0-2", "0"))

idw_depCd$scenario <- factor(idw_depCd$scenario,
                         levels = c("BNPR", "BNPRLopt", "BNPRLopt(dep)"))

idw_dep_spread <- idw_depCd[, -5] %>% 
  spread(key = scenario, value = var1.pred)

plot_dep <- ggplot()+
  geom_raster(data=idw_depCd, aes(x=x, y=y, fill=range))+
  geom_sf(data = QYBorder, color="black")+
  scale_fill_locuszoom(name = "Deposition Cd input")+
  facet_wrap(~scenario)+
  labs(title ="(b)")+
  theme_void()+
  theme(plot.title = element_text(hjust = 0),
        strip.text = element_blank(),
        text = element_text(size = 16, family="serif"))+
  coord_sf(crs=st_crs(QY_rast))

plot_man/plot_dep

# ggsave("Figures/Figure_5.pdf", plot_man/plot_dep,
#        width = 10, 
#        height = 6,
#        device = cairo_pdf)

manure_Cd_long <- manure_Cd_sf %>%
  st_drop_geometry() %>%
  pivot_longer(
    cols = -ID,
    names_to = "scenario",
    values_to = "Cd_input_g_ha_yr"
  ) %>% 
  mutate(source = "manure")

deposition_Cd_long <- deposition_Cd_sf %>%
  st_drop_geometry() %>%
  pivot_longer(
    cols = -ID,
    names_to = "scenario",
    values_to = "Cd_input_g_ha_yr"
  )%>% 
  mutate(source = "deposition")

man_dep_Cd_long <- manure_Cd_long %>% 
  bind_rows(deposition_Cd_long)

# write.csv(man_dep_Cd_long,
#           "Figure_Source_Data/SourceData_Fig5.csv", row.names = FALSE)

```

## 3.2 Spatial variations in the required lime application rate under different management scenarios

```{r}
lime_sf <- st_read("spatial_data/spatial_lime_in.shp")

idw_4 <- idw(formula = BNPRLopt1 ~ 1,
             locations = lime_sf,
             newdata = QY_rast,
             idp = 5) %>%
  as.data.frame() %>% dplyr::select(c(1:3)) %>%
  drop_na() %>%
  mutate(range = case_when(var1.pred>=4 ~ ">4",
                           var1.pred<4 & var1.pred>=2 ~  "2-4",
                           var1.pred<2 & var1.pred>=1 ~ "1-2",
                           var1.pred<1& var1.pred>=0.1~ "0-1", 
                           var1.pred<0.1~"Not required"
                           )
         )

idw_4$range <- factor(idw_4$range,
                      levels = c(">4", "2-4", "1-2", "0-1", "Not required"))

idw_6 <- idw(formula =BNPRLopt2~ 1,
             locations = lime_sf,
             newdata = QY_rast, 
             idp = 5) %>% 
  as.data.frame() %>% dplyr::select(c(1:3)) %>% 
  drop_na()%>%
  mutate(range = case_when(var1.pred>=4 ~ ">4",
                           var1.pred<4 & var1.pred>=2 ~  "2-4",
                           var1.pred<2 & var1.pred>=1 ~ "1-2",
                           var1.pred<1& var1.pred>=0.1~ "0-1", 
                           var1.pred<0.1~"Not required"
                           )
         )

idw_6$range <- factor(idw_6$range,
                      levels = c(">4", "2-4", "1-2", "0-1", "Not required"))

idw_lime <- rbind(idw_4 %>% mutate(scenario = "BNPRLopt"), 
                  idw_6 %>% mutate(scenario = "BNPRLopt(dep)"))

idw_lime_spread <- idw_lime[,-4] %>% 
  spread(key = scenario, value = var1.pred)

## generate Figure 6
ggplot()+
  geom_raster(data=idw_lime, aes(x=x, y=y, fill=range))+
  geom_sf(data = QYBorder, color="black")+
  scale_fill_locuszoom(name = expression("Lime input"))+
  facet_wrap(~scenario)+
  theme_void()+
  theme(plot.title = element_text(hjust = 0.5),
        text = element_text(size = 16, family="serif"))+
  coord_sf(crs=st_crs(QY_rast))

# ggsave("Figures/Figure_6.pdf", 
#        width = 10,
#        height = 5.5,
#        device = cairo_pdf)

colnames(lime_sf)[c(2, 3)] <- c("BNPRLopt", "BNPRLopt(dep)")
lime_long <- lime_sf %>%
  st_drop_geometry() %>%
  pivot_longer(
    cols = -ID,
    names_to = "scenario",
    values_to = "lime_input_kg_ha_5_years"
  )

# write.csv(lime_long,
#           "Figure_Source_Data/SourceData_Fig6.csv", row.names = FALSE)


```
